UniScatter: Unifying\\Backscatter Communications, Reconfigurable Intelligent Surface, and Symbiotic Radio

### 2022-08-01 main.tex
:pencil: Update abstract

	\gls{ris} adapts scattering antennas or programmable metamaterial to control propagation environment and enhance signal strength in the desired direction.

@@

	\gls{sr} incorporates scatter nodes into active wireless networks and utilize recycled signal to transmit self information and enhance legacy multipath to the cooperative receiver.

@@

	In this paper, we introduce UniScatter as a novel paradigm that bridges and generalizes those three concepts to support the high throughput, ultralow power, and ubiquitous connectivity of future wireless networks using shared spectrum, energy, and infrastructures.

@@

	Based on \gls{csi}, each UniScatter node adapts probability distribution of reflection states to balance information encoding and passive beamforming in a mutualistic and flexible manner.
	The scatter source of \gls{bc}/\gls{sr} and reflecting element of \gls{ris} can be regarded as extreme cases of UniScatter node, where the input distribution boils down to equiprobable and degenerate, respectively.

@@

	To accommodate signal characteristics, we propose a practical receiver that first semi-coherently decodes all nodes from accumulated energy, then re-encodes and determines the equivalent channel for primary decoding.

@@

	It reduces the complexity of cooperative decoding and preserves the benefit of passive beamforming on primary link.
	Moreover, we consider a scenario where a multi-antenna \gls{ap} serves a single-antenna user surrounded by multiple UniScatter nodes, and characterize the achievable primary-(total-)backscatter rate region by optimizing input distribution at nodes, active beamforming at the \gls{ap}, and decision regions at the user.
	Simulation results demonstrate UniScatter can unify \gls{bc}, \gls{ris} and \gls{sr} to flexibly control transmit-assist tradeoff via smart input distribution design.

>>>>

	\gls{ris} adapts scattering antennas or programmable metamaterial to control propagation environment and boost signal strength in desired direction.

@@

	\gls{sr} incorporates scatter nodes into active networks, which recycle ambient signal to transmit self information and enhance legacy multipath to the cooperative receiver.

@@

	In this paper, we introduce UniScatter as a novel paradigm that bridges and generalizes those three concepts to support the high throughput, ultralow power, and ubiquitous connectivity of future wireless networks.

@@

	% Based on \gls{csi}, each UniScatter node adapts probability distribution of reflection states to balance information encoding and passive beamforming in a mutualistic and flexible manner.
	Using shared spectrum, energy, and infrastructures, each UniScatter node adapts probability distribution of reflection states based on \gls{csi} to balance information encoding and passive beamforming in a mutualistic and flexible manner.
	The scatter source of \gls{bc}/\gls{sr} and reflecting element of \gls{ris} can be viewed as extreme cases of UniScatter node, where the input distribution boils down to equiprobable and degenerate, respectively.

@@

	To accommodate signal characteristics, we propose a practical receiver that semi-coherently decodes all nodes from accumulated energy, re-encodes to determine the equivalent channel, then decodes the primary link.
	% To accommodate signal characteristics, we propose a practical receiver that semi-coherently decodes all nodes from accumulated energy, re-encodes to determine the equivalent channel, and decodes the primary link.
	% To accommodate signal characteristics, we propose a practical receiver that first semi-coherently decodes all nodes by energy detection, then re-encodes and determines the equivalent channel for primary decoding.

@@

	It reduces the complexity of cooperative decoding while preserves the benefit of backscatter modulation and passive beamforming.
	% Moreover, we consider an application scenario where a multi-antenna \gls{ap} serves a single-antenna user surrounded by multiple UniScatter nodes, and characterize the achievable primary-(total-)backscatter rate region by optimizing input distribution at nodes, active beamforming at the \gls{ap}, and decision regions at the user.
	Moreover, we consider an application scenario where a multi-antenna \gls{ap} serves a single-antenna user surrounded by multiple UniScatter nodes, and characterize the achievable primary-(total-)backscatter rate region by designing input distribution at the nodes, active beamforming at the \gls{ap}, and backscatter decision design at the user.
	Simulation results demonstrate UniScatter can unify \gls{bc}, \gls{ris} and \gls{sr} to flexibly control the transmit-assist tradeoff via smart input distribution design.
